---
title: "Tracked indicator association with onward transmission -- EVD in Eastern DRC, 2018-20"
author: 
  - Dean Sayre^[United States Centers for Disease Control and Prevention, omp2@cdc.gov]
date: "`r format(Sys.time(), '%A %d %B %Y')`"
output: 
  html_document:
    code_folding: hide
    code_download: true
    highlight: zenburn
    number_sections: no
    theme: spacelab    
    toc: no
---


```{r setup, include=FALSE}


knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      fig.width = 10, fig.height = 8)

pacman::p_load(EpiEstim, 
               rio, 
               slider,
               tidyverse)

```

# {.tabset}

## Data loading and wrangling

```{r}

linelist <- rio::import(here::here("data", 
                                   "Ebola_North_kivu_10th_outbreak_2018", 
                                   "master_linelist_current - deidentified fo 2026.xlsx"))


ditch_weeks <- map(seq(1,isoweek(min(linelist$onset_calc, na.rm = TRUE))-1,1), 
                   ~paste0(2018, "_W",  str_pad(.x,
                                                side = "left", pad = "0", width = 2))
) %>% 
  append(map(seq(isoweek(max(linelist$onset_calc, na.rm = TRUE))+1, 53), 
             ~paste0(2020, "_W", str_pad(.x, 
                                         side = "left", 
                                         pad = "0", 
                                         width = 2)))
  )

inc_pre <- linelist %>% 
  mutate(date_onset = case_when(is.na(onset_calc) & community_death == 1 & 
                                  !is.na(date_death) ~ date_death - ddays(8), 
                                .default = onset_calc), 
         year = isoyear(date_onset))

years <- unique(inc_pre$year)
years <- years[!is.na(years)]

years_weeks <- map(years, 
         function(x){
           paste0(x, "_W",  str_pad(seq(1,isoweek(paste0(x, "-12-28")), 1),
                                    side = "left", pad = "0", width = 2))
         }
         ) %>% 
  unlist() %>% 
  setdiff(ditch_weeks) %>% 
  as_tibble()

inc_1 <- inc_pre %>% 
  mutate(
         date_onset = ymd(onset_calc), 
         iso_week = paste0(isoyear(onset_calc), "_W", str_pad(isoweek(onset_calc), 
                                                              side = "left",
                                                              pad ="0", 
                                                              width =  2)), 
         isolation_binary = case_when(community_death == 1|delay_admission > 3 ~ "no", 
                                      delay_admission <= 3 ~ "yes")
         ) 
```

This is a boring tab unless you want to dig into the code... see show button (↑→)
if curious

## Country-wide

### Epi curve and estimated reproduction number over time


```{r}

inc <- inc_1 %>% 
  group_by(iso_week) %>% 
  summarise(count = n(), 
            n_community_death = sum(community_death, na.rm = TRUE), 
            community_death_den = sum(!is.na(community_death)), 
            n_isolated_early = sum(isolation_binary == "yes", na.rm = TRUE), 
            isolated_early_den = sum(!is.na(isolation_binary)), 
            n_contact_registered = sum(contact_registered == "yes", na.rm = TRUE), 
            contact_registered_den = sum(contact_registered %in% c("no", "yes"), na.rm = TRUE)) %>% 
  ungroup() %>% 
  right_join(years_weeks, by = c("iso_week" = "value")) %>% 
  mutate(count = case_when(is.na(count) ~ 0, 
                           .default = count), 
         iso_week = factor(iso_week, levels = sort(.$iso_week))) %>% 
  arrange(iso_week) %>% 
  mutate(n = row_number(), 
         community_death_slider = slide_dbl(n_community_death, mean, .before = 2), 
         isolation_slider = slide_dbl(n_isolated_early, mean, .before = 2), 
         contact_slider = slide_dbl(n_contact_registered, mean, .before = 2))

cases_d_i <- inc$count

sequential <- map(list(2,3), 
    function(x){
      window_width <- x
      t_start <- seq(2, 104 - window_width + 1, by = window_width)
      t_end   <- t_start + window_width - 1
      return(list(t_start, t_end))
      }
    )

overlap <- map(list(2,3), 
    function(x){
      window_width <- x
      t_start <- seq(2, 104 - window_width + 1, by = 1)
      t_end   <- t_start + window_width -1
      return(list(t_start, t_end))
      }
    )

options <- append(sequential, overlap) %>% 
  set_names("seq_2", "seq_3", "overlap_2", "overlap_3")


r_est_i_list <-map(options, 
    function(x){
      wallinga_teunis(
        incid = cases_d_i,
        method = "parametric_si", 
        config = list(mean_si = 15.3/7,
                std_si = 7.3/7,
             #   method = "parametric_si",
                n_sim = 100,
                t_start = x[[1]],
                t_end = x[[2]], 
                seed = 3684))
    })


r_est_i_list_cori <-map(options, 
    function(x){
      estimate_R(
        incid = cases_d_i,
        method = "parametric_si", 
        config = list(mean_si = 15.3/7,
                std_si = 7.3/7,
                t_start = x[[1]],
                t_end = x[[2]]))
    }) %>% 
  set_names(map(names(options), ~paste0(.x, "_cori")))

r_est_i_list1 <- append(r_est_i_list, r_est_i_list_cori)

# r_est_i1 <- wallinga_teunis(
#   incid = cases_d_i,
#   method = "parametric_si", 
#   config = list(mean_si = 15.3/7,
#                 std_si = 7.3/7,
#                 method = "parametric_si",
#                 n_sim = 100,
#                 t_start = t_start,
#                 t_end = t_end, 
#                 seed = 3684)
#   )


a <- map(r_est_i_list1, 
    ~as.data.frame(.x[["R"]])[, c("t_start",
                                  "Mean(R)",
                                  "Std(R)", 
                                  "Quantile.0.025(R)",
                                  "Quantile.0.975(R)")]) %>% 
      set_names(names(r_est_i_list1)) %>% 
  bind_rows(.id = "config") %>% 
  mutate(model = case_when(str_detect(config, "_cori") ~ "Cori", 
                           .default = "Wallinga Teunis"), 
         color = str_remove_all(config, "_cori"))

max_n <- max(inc$n)

epi_curve <- ggplot(inc)+
  geom_col(aes(x = n, y = count), fill = "grey", color = "black")+
  theme_minimal()+
  coord_cartesian(xlim = c(0, max_n))+
  labs(x = NULL, 
       y = "Cases", 
       title = "Epidemiological Curve")

b <- ggplot(a)+
  geom_line(aes(x = t_start, 
                y = `Mean(R)`, 
                group = config, 
                color = color, 
                linetype = model), 
            linewidth = 1.2,
            alpha = 0.6)+
  geom_hline(yintercept = 1, linetype = "dashed")+
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, max_n))+
  labs(x = "Week Number", 
       color = "Configuration", 
       linetype = "R Model", 
       title = "Estimated R")

cowplot::plot_grid(epi_curve, NULL, b, ncol = 1, 
                   rel_heights = c(1,-0.05, 1),
                   align = "hv", 
                   axis = "tblr")


```

There are some differences in estimations by method and parameters used 
unsurprisingly, though this is not terribly drastic.

A note on the 'Configuration' colors. The terms 'seq' (sequential) and 'overlap'
refer to the windows used to generate R estimates. The estimations require  time
windows--both start and stop. For the 'seq', these windows abut, but do not share
any weeks/data in common (e.g., Window 1 consists of weeks 1,2, & 3; Window 2 
consists of weeks 4,5, & 6). For those designated 'overlap' there is still a 
window, but estimates are generated for each week, meaning that data are shared
across multiple estimates (e.g., Window 1 = week 1, 2, & 3; Window 2 = week 2, 
3, & 4). The overlap windows produce more granular estimates, but are less 
independent from one another. 

The number refers to the width of the window.

The line type refers to the estimator used to generate the R from documented 
serial interval for EVD (gamma distribution, mean = 15.3 days, 
SD = 7.3 days; Jombart T, Jarvis CI, Mesfin S, et al. The cost of 
insecurity: from flare-up to control of a major Ebola virus disease hotspot 
during the outbreak in the Democratic Republic of the Congo, 2019.
Euro Surveill 2020; 25: 1900735). "Cori" underlies the EpiEstim::estimate_R() 
(Cori, A. et al. A new framework and software to estimate time-varying 
reproduction numbers during epidemics (AJE 2013))

### Indicators over time {.tabset .tabset-pills}

Note that the configuration scheme is the same. In these instances this refers
to the windows and frequency over which indicators are aggregated (e.g., if the
Rt is estimated using weeks 3, 4, & 5, indicators are also aggregated over those
weeks).

```{r}

# code to lag indicators relative to Rt estimates, but not to be done here


#  test <- map(options, 
#      ~map2(.x[[1]], .x[[2]], 
#            function(a,b) {
#              
#              gap <- b-a
#              start <- max(a-gap, 1)
#              
#              inc %>% 
#                slice(start:a) %>% 
#                summarise(community_death_prop = sum(n_community_death, na.rm = TRUE)/
#                            sum(community_death_den, na.rm = TRUE), 
#                          isolated_early_prop = sum(n_isolated_early, na.rm = TRUE)/
#                            sum(isolated_early_den, na.rm = TRUE), 
#                          contact_prop = sum(n_contact_registered, na.rm = TRUE)/
#                            sum(contact_registered_den, na.rm = TRUE))
#            }) %>% 
#        bind_rows() %>% 
#        mutate(n = row_number())) %>% 
#    set_names(names(options))


a1 <- map(options, 
    ~map2(.x[[1]], .x[[2]], 
          function(a,b) {
            inc %>% 
              slice(a:b) %>% 
              summarise(community_death_prop = sum(n_community_death, na.rm = TRUE)/
                          sum(community_death_den, na.rm = TRUE), 
                        isolated_early_prop = sum(n_isolated_early, na.rm = TRUE)/
                          sum(isolated_early_den, na.rm = TRUE), 
                        contact_prop = sum(n_contact_registered, na.rm = TRUE)/
                          sum(contact_registered_den, na.rm = TRUE))
          }) %>% 
      bind_rows() %>% 
      mutate(n = row_number())) %>% 
  set_names(names(options))


graph_indicator <- map2(a1, map(options, ~tibble(x = pluck(.x, 1)) %>% 
                       mutate(n = row_number())), 
     ~left_join(.x, .y, by = "n")) %>% 
  bind_rows(.id = "algo")

```

#### Community Deaths

```{r}

ggplot(graph_indicator)+
  geom_line(aes(x = x, y = community_death_prop, 
                group = algo, color = algo))+  
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, 104))+
  labs(x = "Week Number", 
       y = "Proportion of New Cases",
       color = "Configuration", 
       title = NULL)
  

```


#### Known contact of case at time of diagnosis

```{r}

ggplot(graph_indicator)+
  geom_line(aes(x = x, y = contact_prop, group = algo, color = algo))+
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, 104))+
  labs(x = "Week Number", 
       y = "Proportion of New Cases",
       color = "Configuration", 
       title = NULL)



```

#### Early Isolation

```{r}

ggplot(graph_indicator)+
  geom_line(aes(x = x, y = isolated_early_prop, group = algo, color = algo))+
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, 104))+
  labs(x = "Week Number", 
       y = "Proportion of New Cases",
       color = "Configuration", 
       title = NULL)


```




```{r}


inc_prov <- inc_1 %>% 
  filter(province != "unknown") %>% 
  split(.$province) %>% 
  map(~.x %>% 
  group_by(iso_week) %>% 
  summarise(count = n(), 
            n_community_death = sum(community_death, na.rm = TRUE), 
            community_death_den = sum(!is.na(community_death)), 
            n_isolated_early = sum(isolation_binary == "yes", na.rm = TRUE), 
            isolated_early_den = sum(!is.na(isolation_binary)), 
            n_contact_registered = sum(contact_registered == "yes", na.rm = TRUE), 
            contact_registered_den = sum(contact_registered %in% c("no", "yes"), 
                                         na.rm = TRUE)) %>% 
  ungroup() %>% 
  right_join(years_weeks, by = c("iso_week" = "value")) %>% 
  mutate(count = case_when(is.na(count) ~ 0, 
                           .default = count), 
         iso_week = factor(iso_week, levels = sort(.$iso_week))) %>% 
  arrange(iso_week) %>% 
  mutate(n = row_number())
  )


r_est_prov_list <-map(inc_prov, 
                   function(y)
                     {map(options, 
                          function(x){
                            wallinga_teunis(
                              incid = y$count,
                              method = "parametric_si", 
                              config = list(mean_si = 15.3/7,
                                            std_si = 7.3/7,
                                            n_sim = 100,
                                            t_start = x[[1]],
                                            t_end = x[[2]], 
                                            seed = 3684))
                            })})

r_est_prov_list_cori <-map(inc_prov, 
                   function(y)
                     {map(options, 
                          function(x){
                            estimate_R(
                              incid = y$count,
                              method = "parametric_si", 
                              config = list(mean_si = 15.3/7,
                                            std_si = 7.3/7,
                                            t_start = x[[1]],
                                            t_end = x[[2]]))
                            }) %>% 
                       set_names(map(names(options), ~paste0(.x, "_cori")))
                   })

r_prov_list <- map2(r_est_prov_list, r_est_prov_list_cori, append)


province_plots <- map2(r_prov_list,
          inc_prov,
         function(x, z){
           prov_db <- map(x, 
                          function(y){
                            as.data.frame(y[["R"]])[, c("t_start",
                                  "Mean(R)",
                                  "Std(R)", 
                                  "Quantile.0.025(R)",
                                  "Quantile.0.975(R)")]}) %>%
             set_names(names(.)) %>% 
             bind_rows(.id = "config") %>% 
             mutate(model = case_when(str_detect(config, "_cori") ~ "Cori", 
                           .default = "Wallinga Teunis"), 
                    color = str_remove_all(config, "_cori"))
           
           
           epi_curve <- ggplot(z)+
  geom_col(aes(x = n, y = count), fill = "grey", color = "black")+
  theme_minimal()+
  coord_cartesian(xlim = c(0, 104))+
  labs(x = NULL, 
       y = "Cases", 
       title = "Epidemiological Curve")
           
           b <- ggplot(prov_db)+
             geom_line(aes(x = t_start, 
                y = `Mean(R)`, 
                group = config, 
                color = color, 
                linetype = model), 
            linewidth = 1.2,
            alpha = 0.6)+
  geom_hline(yintercept = 1, linetype = "dashed")+
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, max_n))+
  labs(x = "Week Number", 
       color = "Configuration", 
       linetype = "Model",
       title = "Estimated R")

cowplot::plot_grid(epi_curve, NULL, b, ncol = 1, 
                   rel_heights = c(1,-0.05, 1),
                   align = "hv", 
                   axis = "tblr")  
})
  
```


## By Province {.tabset}

### Epi curve and estimated reproduction number over time {.tabset.tabset-pills}

#### Ituri
```{r}
province_plots[["ituri"]]
```

#### North Kivu

```{r}
province_plots[["nord_kivu"]]
```



### Indicators over time {.tabset.tabset-pills}

```{r}
inc_prov

a2 <- map(options, 
          ~map2(.x[[1]], .x[[2]], 
                
                      function(a,b) {
                        inc_prov[[1]] %>% 
                          slice(a:b) %>% 
                          summarise(community_death_prop = sum(n_community_death, 
                                                               na.rm = TRUE)/
                                      sum(community_death_den, na.rm = TRUE), 
                                    isolated_early_prop = sum(n_isolated_early, 
                                                              na.rm = TRUE)/
                                      sum(isolated_early_den, na.rm = TRUE), 
                                    contact_prop = sum(n_contact_registered, 
                                                       na.rm = TRUE)/
                                      sum(contact_registered_den, na.rm = TRUE))
                        }) %>% 
      bind_rows() %>% 
      mutate(n = row_number()) %>% 
  set_names(names(options)))


graph_indicator <- map2(a1, map(options, ~tibble(x = pluck(.x, 1)) %>% 
                       mutate(n = row_number())), 
     ~left_join(.x, .y, by = "n")) %>% 
  bind_rows(.id = "algo")

```



```{r}

inc_zone <- inc_1 %>% 
  mutate(name = paste0(province, "_", zone_de_sante)) %>% 
  filter(name != "unknown_nyankunde") %>% 
  split(.$name) %>% 
  map(~.x %>% 
  group_by(iso_week) %>% 
  summarise(count = n(), 
            n_community_death = sum(community_death, na.rm = TRUE)/sum(!is.na(community_death)), 
            n_isolated_early = sum(isolation_binary == "yes", na.rm = TRUE)/sum(!is.na(isolation_binary)), 
            n_contact_registered = sum(contact_registered == "yes", na.rm = TRUE)/
              sum(contact_registered %in% c("no", "yes"), na.rm = TRUE)) %>% 
  ungroup() %>% 
  right_join(years_weeks, by = c("iso_week" = "value")) %>% 
  mutate(count = case_when(is.na(count) ~ 0, 
                           .default = count), 
         iso_week = factor(iso_week, levels = sort(.$iso_week))) %>% 
  arrange(iso_week) %>% 
  mutate(n = row_number(), 
         community_death_slider = slide_dbl(n_community_death, mean, .before = 2), 
         isolation_slider = slide_dbl(n_isolated_early, mean, .before = 2), 
         contact_slider = slide_dbl(n_contact_registered, mean, .before = 2))
  )

zone_remove <- map(inc_zone, 
      ~.x %>% 
      summarise(weeks_w_cases = sum(count != 0))) %>% 
  bind_rows(.id = "name") %>% 
  filter(weeks_w_cases < 5)

inc_zone1 <- inc_zone %>% 
  discard_at(zone_remove$name)

r_est_zone_list <-map(inc_zone1, 
                   function(y)
                     {map(options, 
                          function(x){
                            estimate_R(
                              incid = y$count,
                              method = "parametric_si", 
                              config = make_config(list(mean_si = 15.3/7,
                                            std_si = 7.3/7,
                                          #  method = "parametric_si",
                                          #  n_sim = 100,
                                            t_start = x[[1]],
                                            t_end = x[[2]]
                                           # seed = 3684
                                          )))
                            })})



zone_plots <- map2(r_est_zone_list,
          inc_zone1,
         function(x, z){
           prov_db <- map(x, 
                          function(y){
                            as.data.frame(y[["R"]])[, c("t_start",
                                  "Mean(R)",
                                  "Std(R)", 
                                  "Quantile.0.025(R)",
                                  "Quantile.0.975(R)")]}) %>%
             set_names(names(.)) %>% 
             bind_rows(.id = "config")
           
           
           epi_curve <- ggplot(z)+
  geom_col(aes(x = n, y = count), fill = "grey", color = "black")+
  theme_minimal()+
  coord_cartesian(xlim = c(0, 104))+
  labs(x = NULL, 
       y = "Cases", 
       title = "Epidemiological Curve")
           
           b <- ggplot(prov_db)+
             geom_line(aes(x = t_start, 
                y = `Mean(R)`, 
                group = config, 
                color = config), 
            linewidth = 1.2,
            alpha = 0.6)+
  geom_hline(yintercept = 1, linetype = "dashed")+
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, max_n))+
  labs(x = "Week Number", 
       color = "Configuration", 
       title = "Estimated R")

cowplot::plot_grid(epi_curve, NULL, b, ncol = 1, 
                   rel_heights = c(1,-0.05, 1),
                   align = "hv", 
                   axis = "tblr")  
})



```

