---
title: "Tracked indicator association with onward transmission -- EVD in Eastern DRC, 2018-20"
author: 
  - Dean Sayre^[United States Centers for Disease Control and Prevention, omp2@cdc.gov]
date: "`r format(Sys.time(), '%A %d %B %Y')`"
output: 
  html_document:
    code_folding: hide
    code_download: true
    highlight: zenburn
    number_sections: no
    theme: spacelab    
    toc: no
---


```{r setup, include=FALSE}


knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      fig.width = 10, fig.height = 8)

pacman::p_load(EpiEstim, 
               rio, 
               slider,
               forecast,
               glmmTMB,
               tidyverse)

```

# {.tabset}

## Data loading and wrangling

```{r}

linelist <- rio::import(here::here("data", 
                                   "Ebola_North_kivu_10th_outbreak_2018", 
                                   "master_linelist_current - deidentified fo 2026.xlsx"))


ditch_weeks <- map(seq(1,isoweek(min(linelist$onset_calc, na.rm = TRUE))-1,1), 
                   ~paste0(2018, "_W",  str_pad(.x,
                                                side = "left", pad = "0", width = 2))
) %>% 
  append(map(seq(isoweek(max(linelist$onset_calc, na.rm = TRUE))+1, 53), 
             ~paste0(2020, "_W", str_pad(.x, 
                                         side = "left", 
                                         pad = "0", 
                                         width = 2)))
  )

inc_pre <- linelist %>% 
  mutate(date_onset = case_when(is.na(onset_calc) & community_death == 1 & 
                                  !is.na(date_death) ~ date_death - ddays(8), 
                                .default = onset_calc), 
         year = isoyear(date_onset))

years <- unique(inc_pre$year)
years <- years[!is.na(years)]

years_weeks <- map(years, 
         function(x){
           paste0(x, "_W",  str_pad(seq(1,isoweek(paste0(x, "-12-28")), 1),
                                    side = "left", pad = "0", width = 2))
         }
         ) %>% 
  unlist() %>% 
  setdiff(ditch_weeks) %>% 
  as_tibble()

inc_1 <- inc_pre %>% 
  mutate(
         date_onset = ymd(onset_calc), 
         iso_week = paste0(isoyear(onset_calc), "_W", str_pad(isoweek(onset_calc), 
                                                              side = "left",
                                                              pad ="0", 
                                                              width =  2)), 
         isolation_binary = case_when(community_death == 1|delay_admission > 3 ~ "no", 
                                      delay_admission <= 3 ~ "yes")
         ) 
```

This is a boring tab unless you want to dig into the code... see show button (↑→)
if curious

## Country-wide

### Epi curve and estimated reproduction number over time


```{r}

inc <- inc_1 %>% 
  group_by(iso_week) %>% 
  summarise(count = n(), 
            n_community_death = sum(community_death, na.rm = TRUE), 
            community_death_den = sum(!is.na(community_death)), 
            n_isolated_early = sum(isolation_binary == "yes", na.rm = TRUE), 
            isolated_early_den = sum(!is.na(isolation_binary)), 
            n_contact_registered = sum(contact_registered == "yes", na.rm = TRUE), 
            contact_registered_den = sum(contact_registered %in% c("no", "yes"), na.rm = TRUE)) %>% 
  ungroup() %>% 
  right_join(years_weeks, by = c("iso_week" = "value")) %>% 
  mutate(count = case_when(is.na(count) ~ 0, 
                           .default = count), 
         iso_week = factor(iso_week, levels = sort(.$iso_week))) %>% 
  arrange(iso_week) %>% 
  mutate(n = row_number(), 
         community_death_slider = slide_dbl(n_community_death, mean, .before = 2), 
         isolation_slider = slide_dbl(n_isolated_early, mean, .before = 2), 
         contact_slider = slide_dbl(n_contact_registered, mean, .before = 2))

cases_d_i <- inc$count

sequential <- map(list(2,3), 
    function(x){
      window_width <- x
      t_start <- seq(2, 104 - window_width + 1, by = window_width)
      t_end   <- t_start + window_width - 1
      return(list(t_start, t_end))
      }
    )

overlap <- map(list(2,3), 
    function(x){
      window_width <- x
      t_start <- seq(2, 104 - window_width + 1, by = 1)
      t_end   <- t_start + window_width -1
      return(list(t_start, t_end))
      }
    )

options <- append(sequential, overlap) %>% 
  set_names("seq_2", "seq_3", "overlap_2", "overlap_3")


r_est_i_list <-map(options, 
    function(x){
      wallinga_teunis(
        incid = cases_d_i,
        method = "parametric_si", 
        config = list(mean_si = 15.3/7,
                std_si = 7.3/7,
             #   method = "parametric_si",
                n_sim = 100,
                t_start = x[[1]],
                t_end = x[[2]], 
                seed = 3684))
    })


r_est_i_list_cori <-map(options, 
    function(x){
      estimate_R(
        incid = cases_d_i,
        method = "parametric_si", 
        config = list(mean_si = 15.3/7,
                std_si = 7.3/7,
                t_start = x[[1]],
                t_end = x[[2]]))
    }) %>% 
  set_names(map(names(options), ~paste0(.x, "_cori")))

r_est_i_list1 <- append(r_est_i_list, r_est_i_list_cori)

# r_est_i1 <- wallinga_teunis(
#   incid = cases_d_i,
#   method = "parametric_si", 
#   config = list(mean_si = 15.3/7,
#                 std_si = 7.3/7,
#                 method = "parametric_si",
#                 n_sim = 100,
#                 t_start = t_start,
#                 t_end = t_end, 
#                 seed = 3684)
#   )


r_nation <- map(r_est_i_list1, 
    ~as.data.frame(.x[["R"]])[, c("t_start",
                                  "Mean(R)",
                                  "Std(R)", 
                                  "Quantile.0.025(R)",
                                  "Quantile.0.975(R)")]) %>% 
      set_names(names(r_est_i_list1)) %>% 
  bind_rows(.id = "config") %>% 
  mutate(model = case_when(str_detect(config, "_cori") ~ "Cori", 
                           .default = "Wallinga Teunis"), 
         color = str_remove_all(config, "_cori"))

max_n <- max(inc$n)

epi_curve <- ggplot(inc)+
  geom_col(aes(x = n, y = count), fill = "grey", color = "black")+
  theme_minimal()+
  coord_cartesian(xlim = c(0, max_n))+
  labs(x = NULL, 
       y = "Cases", 
       title = "Epidemiological Curve")

b <- ggplot(r_nation)+
  geom_line(aes(x = t_start, 
                y = `Mean(R)`, 
                group = config, 
                color = color, 
                linetype = model), 
            linewidth = 1.2,
            alpha = 0.6)+
  geom_hline(yintercept = 1, linetype = "dashed")+
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, max_n))+
  labs(x = "Week Number", 
       color = "Configuration", 
       linetype = "R Model", 
       title = "Estimated R")

cowplot::plot_grid(epi_curve, NULL, b, ncol = 1, 
                   rel_heights = c(1,-0.05, 1),
                   align = "hv", 
                   axis = "tblr")


```

There are some differences in estimations by method and parameters used 
unsurprisingly, though this is not terribly drastic.

A note on the 'Configuration' colors. The terms 'seq' (sequential) and 'overlap'
refer to the windows used to generate R estimates. The estimations require  time
windows--both start and stop. For the 'seq', these windows abut, but do not share
any weeks/data in common (e.g., Window 1 consists of weeks 1,2, & 3; Window 2 
consists of weeks 4,5, & 6). For those designated 'overlap' there is still a 
window, but estimates are generated for each week, meaning that data are shared
across multiple estimates (e.g., Window 1 = week 1, 2, & 3; Window 2 = week 2, 
3, & 4). The overlap windows produce more granular estimates, but are less 
independent from one another. 

The number refers to the width of the window.

The line type refers to the estimator used to generate the R from documented 
serial interval for EVD (gamma distribution, mean = 15.3 days, 
SD = 7.3 days; Jombart T, Jarvis CI, Mesfin S, et al. The cost of 
insecurity: from flare-up to control of a major Ebola virus disease hotspot 
during the outbreak in the Democratic Republic of the Congo, 2019.
Euro Surveill 2020; 25: 1900735). "Cori" underlies the EpiEstim::estimate_R() 
(Cori, A. et al. A new framework and software to estimate time-varying 
reproduction numbers during epidemics (AJE 2013))

### Indicators over time {.tabset .tabset-pills}

Note that the configuration scheme is the same. In these instances this refers
to the windows and frequency over which indicators are aggregated (e.g., if the
Rt is estimated using weeks 3, 4, & 5, indicators are also aggregated over those
weeks).

```{r}

# code to lag indicators relative to Rt estimates, but not to be done here


#  test <- map(options, 
#      ~map2(.x[[1]], .x[[2]], 
#            function(a,b) {
#              
#              gap <- b-a
#              start <- max(a-gap, 1)
#              
#              inc %>% 
#                slice(start:a) %>% 
#                summarise(community_death_prop = sum(n_community_death, na.rm = TRUE)/
#                            sum(community_death_den, na.rm = TRUE), 
#                          isolated_early_prop = sum(n_isolated_early, na.rm = TRUE)/
#                            sum(isolated_early_den, na.rm = TRUE), 
#                          contact_prop = sum(n_contact_registered, na.rm = TRUE)/
#                            sum(contact_registered_den, na.rm = TRUE))
#            }) %>% 
#        bind_rows() %>% 
#        mutate(n = row_number())) %>% 
#    set_names(names(options))


a1 <- map(options, 
    ~map2(.x[[1]], .x[[2]], 
          function(a,b) {
            inc %>% 
              slice(a:b) %>% 
              summarise(community_death_prop = sum(n_community_death, na.rm = TRUE)/
                          sum(community_death_den, na.rm = TRUE), 
                        isolated_early_prop = sum(n_isolated_early, na.rm = TRUE)/
                          sum(isolated_early_den, na.rm = TRUE), 
                        contact_prop = sum(n_contact_registered, na.rm = TRUE)/
                          sum(contact_registered_den, na.rm = TRUE))
          }) %>% 
      bind_rows() %>% 
      mutate(n = row_number())) %>% 
  set_names(names(options))


graph_indicator_nation <- map2(a1, map(options, ~tibble(x = pluck(.x, 1)) %>% 
                       mutate(n = row_number())), 
     ~left_join(.x, .y, by = "n")) %>% 
  bind_rows(.id = "algo")

```

#### Community Deaths

```{r}

ggplot(graph_indicator)+
  geom_line(aes(x = x, y = community_death_prop, 
                group = algo, color = algo), 
            linewidth = 1.2,
            alpha = 0.6)+  
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, 104))+
  labs(x = "Week Number", 
       y = "Proportion of New Cases",
       color = "Configuration", 
       title = NULL)
  

```


#### Known contact of case at time of diagnosis

```{r}

ggplot(graph_indicator)+
  geom_line(aes(x = x, y = contact_prop, group = algo, color = algo), 
            linewidth = 1.2,
            alpha = 0.6)+  
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, 104))+
  labs(x = "Week Number", 
       y = "Proportion of New Cases",
       color = "Configuration", 
       title = NULL)



```

#### Early Isolation

```{r}

ggplot(graph_indicator)+
  geom_line(aes(x = x, y = isolated_early_prop, group = algo, color = algo), 
            linewidth = 1.2,
            alpha = 0.6)+  
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, 104))+
  labs(x = "Week Number", 
       y = "Proportion of New Cases",
       color = "Configuration", 
       title = NULL)


```



```{r}

inc_prov <- inc_1 %>% 
  filter(province != "unknown") %>% 
  split(.$province) %>% 
  map(~.x %>% 
  group_by(iso_week) %>% 
  summarise(count = n(), 
            n_community_death = sum(community_death, na.rm = TRUE), 
            community_death_den = sum(!is.na(community_death)), 
            n_isolated_early = sum(isolation_binary == "yes", na.rm = TRUE), 
            isolated_early_den = sum(!is.na(isolation_binary)), 
            n_contact_registered = sum(contact_registered == "yes", na.rm = TRUE), 
            contact_registered_den = sum(contact_registered %in% c("no", "yes"), 
                                         na.rm = TRUE)) %>% 
  ungroup() %>% 
  right_join(years_weeks, by = c("iso_week" = "value")) %>% 
  mutate(count = case_when(is.na(count) ~ 0, 
                           .default = count), 
         iso_week = factor(iso_week, levels = sort(.$iso_week))) %>% 
  arrange(iso_week) %>% 
  mutate(n = row_number())
  )


r_est_prov_list <-map(inc_prov, 
                   function(y)
                     {map(options, 
                          function(x){
                            wallinga_teunis(
                              incid = y$count,
                              method = "parametric_si", 
                              config = list(mean_si = 15.3/7,
                                            std_si = 7.3/7,
                                            n_sim = 100,
                                            t_start = x[[1]],
                                            t_end = x[[2]], 
                                            seed = 3684))
                            })})

r_est_prov_list_cori <-map(inc_prov, 
                   function(y)
                     {map(options, 
                          function(x){
                            estimate_R(
                              incid = y$count,
                              method = "parametric_si", 
                              config = list(mean_si = 15.3/7,
                                            std_si = 7.3/7,
                                            t_start = x[[1]],
                                            t_end = x[[2]]))
                            }) %>% 
                       set_names(map(names(options), ~paste0(.x, "_cori")))
                   })

r_prov_list <- map2(r_est_prov_list, r_est_prov_list_cori, append)


province_plots <- map2(r_prov_list,
          inc_prov,
         function(x, z){
           prov_db <- map(x, 
                          function(y){
                            as.data.frame(y[["R"]])[, c("t_start",
                                  "Mean(R)",
                                  "Std(R)", 
                                  "Quantile.0.025(R)",
                                  "Quantile.0.975(R)")]}) %>%
             set_names(names(.)) %>% 
             bind_rows(.id = "config") %>% 
             mutate(model = case_when(str_detect(config, "_cori") ~ "Cori", 
                           .default = "Wallinga Teunis"), 
                    color = str_remove_all(config, "_cori"))
           
           
           epi_curve <- ggplot(z)+
  geom_col(aes(x = n, y = count), fill = "grey", color = "black")+
  theme_minimal()+
  coord_cartesian(xlim = c(0, 104))+
  labs(x = NULL, 
       y = "Cases", 
       title = "Epidemiological Curve")
           
           b <- ggplot(prov_db)+
             geom_line(aes(x = t_start, 
                y = `Mean(R)`, 
                group = config, 
                color = color, 
                linetype = model), 
            linewidth = 1.2,
            alpha = 0.6)+
  geom_hline(yintercept = 1, linetype = "dashed")+
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, max_n))+
  labs(x = "Week Number", 
       color = "Configuration", 
       linetype = "Model",
       title = "Estimated R")

cowplot::plot_grid(epi_curve, NULL, b, ncol = 1, 
                   rel_heights = c(1,-0.05, 1),
                   align = "hv", 
                   axis = "tblr")  
})
  
```


## By Province {.tabset}

### Epi curve and estimated reproduction number over time {.tabset}

#### Ituri
```{r}
province_plots[["ituri"]]
```

#### North Kivu

```{r}
province_plots[["nord_kivu"]]
```


### Indicators over time {.tabset}

```{r}

a2 <- map(inc_prov, 
          function(a1){
            map(options, 
          ~map2(.x[[1]], .x[[2]], 
                
                      function(a,b) {
                        
                        a1 %>% 
                          slice(a:b) %>% 
                          summarise(community_death_prop = sum(n_community_death, 
                                                               na.rm = TRUE)/
                                      sum(community_death_den, na.rm = TRUE), 
                                    isolated_early_prop = sum(n_isolated_early, 
                                                              na.rm = TRUE)/
                                      sum(isolated_early_den, na.rm = TRUE), 
                                    contact_prop = sum(n_contact_registered, 
                                                       na.rm = TRUE)/
                                      sum(contact_registered_den, na.rm = TRUE))
                        }) %>% 
      bind_rows() %>% 
      mutate(n = row_number()))
            }
      )


graph_indicator_prov <- map(a2, 
                       ~map2(.x, map(options, ~tibble(x = pluck(.x, 1)) %>% 
                       mutate(n = row_number())), 
     ~left_join(.x, .y, by = "n")) %>% 
  bind_rows(.id = "algo"))


ind_graph <- function(db, x = x, ind, group = algo){
  
  ggplot(db)+
  geom_line(aes(x = x, y = .data[[ind]],
                group = algo, 
                color = algo), 
            linewidth = 1.2,
            alpha = 0.6)+  
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, 104))+
  labs(x = "Week Number", 
       y = "Proportion of New Cases",
       color = "Configuration", 
       title = NULL)
}

```


#### Ituri {.tabset .tabset-pills}

##### Community Deaths
```{r}

db <- graph_indicator_prov[["ituri"]]

ind_graph(db, ind = "community_death_prop")

```

##### Known Contact

```{r}

ind_graph(db, ind = "contact_prop")

```


##### Early Isolation

```{r}

ind_graph(db, ind = "isolated_early_prop")

```


#### North Kivu {.tabset .tabset-pills}

##### Community Deaths
```{r}

db <- graph_indicator_prov[["nord_kivu"]]

ind_graph(db, ind = "community_death_prop")

```

##### Known Contact

```{r}

ind_graph(db, ind = "contact_prop")

```


##### Early Isolation

```{r}

ind_graph(db, ind = "isolated_early_prop")

```


## By Health Zone {.tabset}

```{r}

inc_zone <- inc_1 %>% 
  mutate(name = paste0(province, "_", zone_de_sante)) %>% 
  filter(name != "unknown_nyankunde") %>% 
  split(.$name) %>% 
  map(~.x %>% 
  group_by(iso_week) %>% 
  summarise(count = n(), 
            n_community_death = sum(community_death, na.rm = TRUE), 
            community_death_den = sum(!is.na(community_death)), 
            n_isolated_early = sum(isolation_binary == "yes", na.rm = TRUE), 
            isolated_early_den = sum(!is.na(isolation_binary)), 
            n_contact_registered = sum(contact_registered == "yes", na.rm = TRUE), 
            contact_registered_den = sum(contact_registered %in% c("no", "yes"), 
                                         na.rm = TRUE)) %>% 
  ungroup() %>% 
  right_join(years_weeks, by = c("iso_week" = "value")) %>% 
  mutate(count = case_when(is.na(count) ~ 0, 
                           .default = count), 
         iso_week = factor(iso_week, levels = sort(.$iso_week))) %>% 
  arrange(iso_week) %>% 
  mutate(n = row_number())
  )

zone_remove <- map(inc_zone, 
      ~.x %>% 
      summarise(weeks_w_cases = sum(count != 0))) %>% 
  bind_rows(.id = "name") %>% 
  filter(weeks_w_cases < 5)

inc_zone1 <- inc_zone %>% 
  discard_at(zone_remove$name)

r_est_zone_list_wt <-map(inc_zone1, 
                   function(y)
                     {map(options, 
                          function(x){
                            wallinga_teunis(
                              incid = cases_d_i,
                              method = "parametric_si", 
                              config = list(mean_si = 15.3/7,
                                            std_si = 7.3/7,
                                            n_sim = 100,
                                            t_start = x[[1]],
                                            t_end = x[[2]], 
                                            seed = 3684))
                            })})

r_est_zone_list_cori <-map(inc_zone1, 
                   function(y)
                     {map(options, 
                          function(x){
                            estimate_R(
                              incid = y$count,
                              method = "parametric_si", 
                              config = make_config(list(mean_si = 15.3/7,
                                            std_si = 7.3/7,
                                            t_start = x[[1]],
                                            t_end = x[[2]])))
                            }) %>% 
                       set_names(~paste(.x, "_cori"))
                     })


r_est_zone_list <- map2(r_est_zone_list_wt, r_est_zone_list_cori, 
                        append)



zone_plots <- map2(r_est_zone_list,
                   inc_zone1,
                   
                   function(x, z){
                     prov_db <- map(x, 
                                    function(y){
                                      as.data.frame(y[["R"]])[, c("t_start",
                                  "Mean(R)",
                                  "Std(R)", 
                                  "Quantile.0.025(R)",
                                  "Quantile.0.975(R)")]}
                                  ) %>%
                       set_names(names(.)) %>% 
                       bind_rows(.id = "config") %>% 
                       mutate(model = case_when(str_detect(config, "_cori") ~ "Cori", 
                                                .default = "Wallinga Teunis"), 
                              color = str_trim(str_remove_all(config, "_cori")))
           
           
           epi_curve <- ggplot(z)+
             geom_col(aes(x = n, y = count), fill = "grey", color = "black")+
             theme_minimal()+
             coord_cartesian(xlim = c(0, 104))+
             labs(x = NULL, 
                  y = "Cases", 
                  title = "Epidemiological Curve")
           
           b <- ggplot(prov_db)+
             geom_line(aes(x = t_start, 
                y = `Mean(R)`, 
                group = config, 
                color = color, 
                linetype = model), 
                linewidth = 1.2,
                alpha = 0.6)+
  geom_hline(yintercept = 1, linetype = "dashed")+
  scale_color_manual(values = c("#a07157", 
                                "#849BA1", 
                                "#b0dbe2", 
                                "#a7568f"))+
  theme_minimal()+
  coord_cartesian(xlim = c(0, max_n))+
  labs(x = "Week Number", 
       color = "Configuration", 
       linetype = "Model",
       title = "Estimated R")

cowplot::plot_grid(epi_curve, NULL, b, ncol = 1, 
                   rel_heights = c(1,-0.05, 1),
                   align = "hv", 
                   axis = "tblr")  
})

a3 <- map(inc_zone1, 
          function(a1){
            map(options, 
          ~map2(.x[[1]], .x[[2]], 
                
                      function(a,b) {
                        
                        a1 %>% 
                          slice(a:b) %>% 
                          summarise(community_death_prop = sum(n_community_death, 
                                                               na.rm = TRUE)/
                                      sum(community_death_den, na.rm = TRUE), 
                                    isolated_early_prop = sum(n_isolated_early, 
                                                              na.rm = TRUE)/
                                      sum(isolated_early_den, na.rm = TRUE), 
                                    contact_prop = sum(n_contact_registered, 
                                                       na.rm = TRUE)/
                                      sum(contact_registered_den, na.rm = TRUE))
                        }) %>% 
      bind_rows() %>% 
      mutate(n = row_number()))
            }
      )


graph_indicator_zs <- map(a3, 
                       ~map2(.x, map(options, ~tibble(x = pluck(.x, 1)) %>% 
                       mutate(n = row_number())), 
                       ~left_join(.x, .y, by = "n")) %>% 
       bind_rows(.id = "algo"))

indicator_panel <- map(graph_indicator_zs, 
    function(db1){
      
      top <- ind_graph(db1, ind = "community_death_prop")
      
      mid <- ind_graph(db1, ind = "contact_prop")
      
      bottom <-  ind_graph(db1, ind = "isolated_early_prop")
      
      out <- cowplot::plot_grid(top, mid, bottom, ncol = 1, 
                         align = "hv", 
                         axis = "tblr", 
                         labels = c("Community Deaths", 
                                    "Known Contacts", 
                                    "Isolated Early"))
      return(out)
      }
    )

plots_out <- map2(zone_plots, indicator_panel, 
     ~cowplot::plot_grid(.x, .y, ncol = 2, align = "hv", axis = "tblr")) %>% 
  set_names(~str_to_title(str_replace_all(.x, "_", " ")))

# flexibly makes tabs graphs made in list form

 make_tab <- function(graph, name) {         
   cat("::: {.panel}\n")                     # Open tab
   cat("###", name, "{.panel-name}\n")       # Label tab
 
   print(graph)                              # Display plot
   
   cat("\n")                                 # Space
   cat(":::\n")                              # Close tab
 }
 

```

```{r results = 'asis'}
walk2(plots_out, names(plots_out), ~make_tab(.x, .y))
```


## Cross Correlation
For assessment of lags in associations

```{r}
library()

wt_2 <- r_nation %>% 
  filter(model == "Wallinga Teunis", config == "seq_2") %>% 
  left_join(graph_indicator_nation %>% 
              filter(algo == "seq_2"), 
            by = c("t_start" = "x"))



non_na_db <- function(db = wt_2, 
                        week = "t_start",
                        var1 = "Mean(R)", 
                        var2){
  
  a <- db %>% 
    filter(!is.na(.data[[var1]]) & !is.na(.data[[var2]])) 
  
  vec0 <- a[[week]]
  vec1 <- a[[var1]]
  vec2 <- a[[var2]]
  
  out <- tibble(week = vec0, 
                R = vec1, 
                ind_prop = vec2)
  
  return(out)
}

lag_corr <- map(list("community_death_prop", 
         "isolated_early_prop", 
         "contact_prop"), 
    function(a){
      non_nas <- non_na_db(var2 = a)
      
      ind <- non_nas$ind_prop
      rt_wt2 <- non_nas$R
      
      fit_x <- auto.arima(ind)
      x_white <- residuals(fit_x)
      
      fit_y <- Arima(rt_wt2, model = fit_x)
      y_white <- residuals(fit_y)
      
      test_white <- Ccf(x_white, y_white, lag.max = 6, plot = FALSE)
      
      out <- tibble(lag = test_white[["lag"]], 
             acf = test_white[["acf"]]) %>% 
        mutate(abs_acf = abs(acf))
             
      return(out)       
    }) %>% 
  set_names("community_death_prop", 
            "isolated_early_prop", 
            "contact_prop")

non_na_1 <- map(list("community_death_prop", 
         "isolated_early_prop", 
         "contact_prop"), 
         
      ~wt_2 %>% 
        select("t_start", "Mean(R)", .x) %>% 
        rename(ind = 3)
    ) %>% 
  set_names("community_death_prop", 
            "isolated_early_prop", 
            "contact_prop") 


test <- map2(non_na_1, 
     list(list(0,2),  
          list(0,2),  
          list(0,4)), 
     function(a,b){
       map(b, 
           function(b1){
             a %>% 
               mutate(lag_ind = lag(ind, n = b1), 
                      rt_lt_1 = case_when(`Mean(R)` < 1 ~ 1, 
                                          `Mean(R)` >= 1 ~ 0, 
                                          .default = NA), 
                      time = factor(t_start, levels = seq(2,94, 2), 
                                    ordered = TRUE))
           })
     })


test1 <- map2(test, 
              list(map(list(0,2), ~paste0("lag_", .x)), 
                   map(list(0,2), ~paste0("lag_", .x)),
                   map(list(0,4), ~paste0("lag_", .x))), 
              function(a,b){
                a %>% 
                  set_names(b)
                })





```

## Modeling for association {.tabset}

### Nation-wide

```{r}


nested_logit_models <- map(test1, 
                           ~map(.x, 
                                function(a){glmmTMB(rt_lt_1 ~ lag_ind + 
                                                      ar1(time + 0 | 1),
                                                    #  (1 | province/health_zone),  
                                                    family = binomial,
                                                    data = a)}
                                )
                           )

summaries <- map(nested_logit_models, 
                           ~map(.x, ~summary(.x))
)

```

### Province-wide

```{r}

ind_prov <- map(graph_indicator_prov,
                ~.x %>% 
                  filter(algo == "seq_2") %>% 
                  select(-c(algo, n))
                  )

                      

prov_r <- map(r_prov_list, 1) %>% 
  map2(ind_prov, 
       ~.x[["R"]] %>% 
        select(t_start, `Mean(R)`) %>% 
         left_join(.y, by = c("t_start" = "x")) %>% 
         mutate(rt_lt_1 = case_when(`Mean(R)` < 1 ~ 1, 
                                          `Mean(R)` >= 1 ~ 0, 
                                          .default = NA)))

time_prov <- map(prov_r, 
    ~tibble(max = max(.x$t_start, na.rm = TRUE), 
            min = min(.x$t_start, na.rm = TRUE))) %>% 
  bind_rows(.id = "prov")


prov_r_with_lag <- map(prov_r, 
                       ~.x %>% 
                         mutate(community_death_prop_lag = lag(community_death_prop, n = 2), 
                                isolated_early_prop_lag = lag(isolated_early_prop, n = 2), 
                                contact_prop_lag = lag(contact_prop, n = 4), 
                                time = factor(t_start, 
                                              levels = seq(min(time_prov$min), 
                                                           max(time_prov$max),
                                                           2), 
                                              ordered = TRUE))) %>% 
  discard_at("sud_kivu") %>% 
  bind_rows(.id = "province")


threshold_grid <- seq(0.1, 0.9, by = 0.05)  

threshold_results <- map(threshold_grid, 
                             function(thresh){
                               map(list("community_death_prop", 
                                           "community_death_prop_lag", 
                                           "isolated_early_prop", 
                                           "isolated_early_prop_lag", 
                                           "contact_prop", 
                                           "contact_prop_lag"), 
                              function(b){
                                db <- prov_r_with_lag %>% 
                                  mutate(above_thresh = as.numeric(.data[[b]] >= thresh))
                                
                                form <- as.formula(paste("rt_lt_1 ~ above_thresh",
                                                         "+ ar1(time + 0 | province)",
                                                         "+ (1 | province)"))
                                model <- tryCatch(
                                  glmmTMB(form, family = binomial,
                                          data = db), 
                                  error = function(e) NULL
                                )
                                
                                if (is.null(model)) return(tibble(threshold = thresh, 
                                                                  aic = NA, 
                                                                  estimate = NA, 
                                                                  p = NA))
                                
                                cc <- summary(model)$coefficients$cond
                                
                                tibble(inidicator = b, 
                                       threshold = thresh,
                                       aic = AIC(model),
                                       estimate = cc["above_thresh", "Estimate"],
                                       p = cc["above_thresh", "Pr(>|z|)"])
                              }     
                                   ) 
                               }
                         ) %>% 
  bind_rows() %>% 
  bind_rows()


nested_logit_models_prov <- map(list("community_death_prop", 
                                           "community_death_prop_lag", 
                                           "isolated_early_prop", 
                                           "isolated_early_prop_lag", 
                                           "contact_prop", 
                                           "contact_prop_lag"), 
                                function(b){
                                        form <- as.formula(
                                          paste0("rt_lt_1 ~", b,
                                                 "+ ar1(time + 0 | province) + 
                                                 (1 | province)"))
                                      glmmTMB(form,  
                                              family = binomial,
                                              data = prov_r_with_lag)}
                                )



threshold_results <- map_dfr(threshold_grid, 
                             function(thresh){
                               df$above_thresh <- as.numeric(df$indicator >= thresh)
                               
                               m <- tryCatch(
    glmmTMB(rt_lt_1 ~ above_thresh + ar1(time + 0 | health_zone) + (1 | province/health_zone),
            family = binomial, data = df),
    error = function(e) NULL
  )
  if (is.null(m)) return(tibble(threshold = thresh, aic = NA, estimate = NA, p = NA))
  
  cc <- summary(m)$coefficients$cond
  tibble(
    threshold = thresh,
    aic = AIC(m),
    estimate = cc["above_thresh", "Estimate"],
    p = cc["above_thresh", "Pr(>|z|)"]
  )
})

threshold_results %>% arrange(aic)


nested_logit_models_prov <- map(list("community_death_prop", 
                                           "community_death_prop_lag", 
                                           "isolated_early_prop", 
                                           "isolated_early_prop_lag", 
                                           "contact_prop", 
                                           "contact_prop_lag"), 
                                      function(b){
                                        form <- as.formula(paste0("rt_lt_1 ~", b,
                                                                  "+ ar1(time + 0 | province) +                                               (1 | province)"))
                                      glmmTMB(form,  
                                              family = binomial,
                                              data = prov_r_with_lag)}
                                )






                           

summaries <- map(nested_logit_models, 
                           ~map(.x, ~summary(.x))
)
```

